Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
Minor intro changes

One note on \emph{accuracy} and \emph{precision:}
In principle, the problem of chemical tagging does not require
absolute accuracy for chemical-abundance measurements.
We only require that we can precisely see that two stars are similar
in their abundances; even if we are wrong about the absolute values of
those abundances.
This point might make it seem like we don't care that our models are
wrong, so long as they are \emph{consistent.}
However, this is a bit misleading:
For chemical tagging to succeed, we need stars with different
atmospheric parameters $(\teff, \logg)$ but the same chemical
abundances to be assigned the same position in chemical-abundance
space.
That doesn't require overall accuracy, but it requires that the models
have the right dependencies on atmospheric parameters such that the
wrongness in abundance space is consistent across the H-R diagram.
That is, we need a substantial amount of accuracy to achieve our goals.

It is important to realize that analysis techniques based on \foreign{ab-initio}
physical models are inaccurate, yet they too strive to improve precision
in the face of knowingly inaccurate models.  Incomplete atomic data, 
simplifications of photospheric structure, presumptions about convective
motions, and inconsistencies resulting from assumptions of the local thermal
equilibrium, all contribute to produce knowingly inaccurate abundances.
\thecannon\ stands out because it demonstrably improves the precision on
chemical abundances, whereas the accuracy of those labels is limited only
by the training set employed.

@@

One final note:
we think of this \documentname\ as performing a proof of concept.
We know that the stellar members of open and globular clusters---stars
that are identified by being close in phase space---contain highly
informative abundance information that identifies them also in
chemical-abundance space.  Does this work the other way around? 
Can chemical tagging identify small subsets of stars, among a vastly
greater background sample, that have a common birth origin? If we 
find stars purely by their clustering in abundance space and subsequently
show that they are part of a still spatially coherent cluster, then
we will have resolved all practical outstanding issues plaguing 
chemical tagging, thereby enabling tantalizing potential to truly
unravel the formation of the Milky Way.

>>>>

One note on \emph{accuracy} and \emph{precision:}
In principle, the problem of chemical tagging does not require
absolute accuracy for chemical-abundance measurements.
We only require that we can precisely see that two stars are similar
in their abundances; even if we are wrong about the absolute values of
those abundances.
This point might make it seem like we don't care that our models are
wrong, so long as they are \emph{consistent.}
However, this is a bit misleading:
For chemical tagging to succeed, we need stars with different
atmospheric parameters $(\teff, \logg)$ but the same chemical
abundances to be assigned the same position in chemical-abundance
space.
That doesn't require overall accuracy, but it requires that the models
have the right dependencies on atmospheric parameters such that the
wrongness in abundance space is consistent across the Hertzsprung-Russell diagram.
That is, we need a substantial amount of accuracy to achieve our goals.

It is important to realize that analysis techniques based on \foreign{ab-initio}
physical models are inaccurate, yet they too strive to improve precision
in the face of knowingly inaccurate models.  Incomplete atomic data, 
simplifications of photospheric structure, presumptions about convective
motion, and inconsistencies resulting from assumptions of the local thermal
equilibrium, all contribute to produce knowingly inaccurate abundances.
\thecannon\ stands out because it demonstrably improves the precision on
chemical abundances, whereas the accuracy of those labels is limited only
by the training set employed.

@@

One final note:
we think of this \documentname\ as performing a proof of concept.
We know that the stellar members of open and globular clusters---stars
that are identified by being close in phase space---contain highly
informative abundance information that identifies them also in
chemical-abundance space.  Does this work the other way around? 
Can chemical tagging identify small subsets of stars, among a vastly
greater background sample, that have a common birth origin? If we 
find stars purely by their clustering in abundance space and subsequently
show that they are part of a still spatially coherent cluster, then
we will have resolved all practical outstanding issues plaguing 
chemical tagging, thereby coming closer to the tantalizing potential 
in truly unravelling the formation of the Milky Way.
